### 2007-01-18 Documentation/appendix.tex
*** empty log message ***

{\tt \@signalerror = 10.:0.0001}. In case of systematics switched on the systematics functions {\tt chiSpectrumTilt}

@@

For the disappearance channels only the QE sample is used since statistics is already quite large and a treatment like for the
appearance channels would only shlightly modify the results. The quantitative treatment of systematics is similar to \cite{Ishitsuka:2005qi}. The following rules are 

@@

The \SPL\ experiment can be simulated with the file {\tt SPL.glb}. This file was used in \cite{Campagne:2006yx}
and follows the experiment description from \cite{Mezzetto:2003mm, Campagne:2004wt}. These references
should be cited if the file {\tt SPL.glb} is used for a scientific publication or a talk. For calculations that
involve {\tt SPL.glb}, the following additional files are required: 
\bi
\item {\tt SPLplus.dat} (neutrino flux from CERN -- $\nu_\mu$)
\item {\tt SPLminus.dat} (neutrino flux from CERN -- $\bar{\nu}_\mu$)
\item {\tt Mig\_WC\_numu.dat} (migration matrix -- $\nu_\mu$)
\item {\tt Mig\_WC\_numubar.dat} (migration matrix -- $\bar{\nu}_\mu$)
\item {\tt Mig\_WC\_nue.dat} (migration matrix -- $\nu_e$)
\item {\tt Mig\_WC\_nuebar.dat} (migration matrix -- $\bar{\nu}_e$)
\item {\tt XCC\_spl.dat} (charged current cross sections)
\item {\tt XNC\_spl.dat} (neutral current cross sections)
\ei
The \SPL\ experiment uses a neutrino beam from the CERN to Fr\'{e}jus. The target power is 
4~MV and 2~years $\nu$-running and 8~years $\bar{\nu}$-running 
is assumed. The fiducial mass of the Water Cerenkov detector is taken to be 
$\mathrm{m_{det} = 500 \,kt}$ at a baseline of L~=~130~km. The energy resolution is introduced manually by
four migration matrices (for $\nu_e , \bar{\nu}_e ,\nu_{\mu} ,\bar{\nu}_\mu$) that describe energy smearing mainly
from Fermi Motion. The following rules are defined within {\tt SPL.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance (+)} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline 
Signal & $1.0 \, \otimes \, (\nu_\mu\rightarrow\nu_\mu)_{\mathrm{CC}}$ & (energy dep. efficiency) & 0.02 & $10^{-4}$\\
 & &  & &\\
Background & $4.3\cdot 10^{-5} \, \otimes \, (\nu_\mu \rightarrow \nu_\mu)_\mathrm{CC}$ & & 0.02 & $10^{-4}$ \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance (+)} &  & \\ \hline
Signal & $0.707 \, \otimes \, (\nu_\mu\rightarrow \nu_e)_\mathrm{CC}$ & & 0.02 & $10^{-4}$\\
&&&&\\
Background & $6.5\cdot 10^{-4} \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & $5.4\cdot 10^{-4} \, \otimes \, (\nu_\mu \rightarrow \nu_\mu)_\mathrm{CC}$ & 0.02 & $10^{-4}$ \\
 & $0.7 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_e )_\mathrm{CC}$ & & 0.02 &  $10^{-4}$ \\
Beam Background & $0.677 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_e )_\mathrm{CC}$ & $0.707 \, \otimes \, (\nu_e \rightarrow \nu_e )_\mathrm{CC}$ & 0.02 & $10^{-4}$ \\ \hline \hline
\multicolumn{3}{|l|}{Disappearance (--)} & & \\ \hline 
Signal & $1.0 \, \otimes \, (\bar{\nu}_\mu\rightarrow\bar{\nu}_\mu)_{\mathrm{CC}}$ & (energy dep. efficiency) & 0.02 & $10^{-4}$\\
 & &  & &\\
Background & $4.3\cdot 10^{-5} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & & 0.02 & $10^{-4}$ \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance (--)} &  & \\ \hline
Signal & $0.677 \, \otimes \, (\bar{\nu}_\mu\rightarrow \bar{\nu}_e)_\mathrm{CC}$ & & 0.02 & $10^{-4}$\\
&&&&\\
Background & $0.0025 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & $5.4\cdot 10^{-4} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & 0.02 & $10^{-4}$ \\
 & $0.7 \, \otimes \, (\nu_\mu \rightarrow \nu_e )_\mathrm{CC}$ & & 0.02 &  $10^{-4}$ \\
Beam Background & $0.677 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_e )_\mathrm{CC}$ & $0.707 \, \otimes \, (\nu_e \rightarrow \nu_e )_\mathrm{CC}$ & 0.02 & $10^{-4}$ \\ \hline \hline
\end{tabular}
\end{center}

@@

The file {\tt Reactor1.glb} allows to simulate a small $\bar{\nu}_e$-disappearance reactor experiment. The basic
version of this file was used within \cite{Huber:2003pm} which should be cited if the file {\tt Reactor1.glb} is
used for a scientific publication or a talk. For calculations that involve {\tt Reactor1.glb}, the following
additional files are required:
\bi
\item {\tt Reactor.dat} (neutrino flux from reactor)
\item {\tt XCCreactor.dat} (charged current cross sections for low energies)
\ei
The neutrino source is the core of a nuclear power reactor. The integrated luminosity is assumed to be
$\mathrm{\mathcal{L} = 400 \,t \, GW\, yr}$, \eg\ a 20~t detector, a reactor with a thermal power of 4~GW
and a running period of 5 years. As detector technology, a liquid scintillator 
detector is assumed, a far detector at a baseline of L~=~1.7~km and a near detector which is
assumed to be identical to the far detector (maybe apart from the size) in order to minimize the impact of systematical uncertainties. The normalization error
used in the file {\tt Reactor1.glb} has to be considered as an effective error, receiving contributions from
individual uncertainties (see~\cite{Huber:2003pm}). The energy resolution is
$\mathrm{\sigma_e=5\%\cdot\sqrt{E_{vis}}}$ and the choice for {\tt sigma\_function} is {\tt \#inverse\_beta}. The following rules are defined within {\tt Reactor1.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline 
Signal & $1.0 \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_{\mathrm{CC}}$ & \hspace{5.5cm} & 0.008 & 0.005\\
 & &  & &\\
Background & $5.8\cdot 10^{-5} \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_\mathrm{CC}$ & \hspace{5.5cm} &
$10^{-6}$ & $10^{-6}$ \\ \hline \hline 
\end{tabular}
\end{center}

@@

The files {\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb} allow to simulate the \DC\ reactor experiment in France. 
The basic versions of these files were used within \cite{Huber:2006vr}, which should be cited if the files 
{\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb} are
used for a scientific publication or a talk. For calculations that involve {\tt D-Chooz\_near.glb} and/or {\tt D-Chooz\_far.glb}, the following
additional files are required:
\bi
\item {\tt Reactor.dat} (neutrino flux from reactor)
\item {\tt XCCreactor.dat} (charged current cross sections for low energies)
\ei
The \DC\ experiment is located at the Chooz reactor complex, and the two reactor cores serve as $\bar{\nu}_e$
neutrino source, so the thermal power is $\mathrm{2\cdot4.2\,GW}$. Two identical liquid scintillator detectors
with a fiducial mass of $\mathrm{m_{det} = 10.16 \,t}$ are used as near and far detector. The far detector
is planned to be located in the {\sc Chooz} cavern at a baseline of L~=~1.05~km from the two reactor cores and
the near detector is assumed to be located at a distance of 0.1~km to the cores. The total running time of the
experiment is assumed to be 5 years. So, the integrated luminosity at the far detector yields $\mathrm{\mathcal{L} \approx
427 \,t \, GW\, yr}$.
Here, the total running time of 5 years is assumed within {\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb}, so near
and far detector are assumed to start the mode of operation simultaneously. For the simulation of \DC\ and
considering a delayed start of data taking at the near detector the file {\tt D-Chooz\_near.glb} has to be
modified. The cancellation of systematical uncertainties is considered by the manual definition of a $\chi^2$
as described in \cite{Huber:2006vr} with the treatment of user-defined systematics as described in \Sec~\ref{sec:userchi}   
The energy resolution is
$\mathrm{\sigma_e=5\%\cdot\sqrt{E_{vis}}}$ and the choice for {\tt sigma\_function} is {\tt \#inverse\_beta}. The following rules are defined within {\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|c|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance} & $\sigma_\mathrm{flux}$ & $\sigma^N_\mathrm{fid}$ & $\sigma^F_\mathrm{fid}$ &
$\sigma^N_\mathrm{cal}$ & $\sigma^F_\mathrm{cal}$ \\ \hline 
Signal & $1.0 \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_{\mathrm{CC}}$ & & 0.02 & 0.006 & 0.006 & 0.005 &
0.005 \\
 & & & & & & & \\
Background & neglected & (sys. dominates) & -- & -- & -- & -- & -- \\ \hline \hline 
\end{tabular}
\end{center}

@@

The $\gamma=100$ $\beta$-beam baseline scenario from CERN to Fr\'{e}jus can be simulated with the file {\tt
BB\_100.glb}. The basic version of this file was used within \cite{Campagne:2006yx}. This reference
should be cited if the file {\tt BB\_100.glb} is used for a scientific publication or a talk. For calculations that
involve {\tt BB\_100.glb}, the following additional files are required: 
\bi
\item {\tt BB100flux\_Ne.dat} ($\beta$-beam neutrino flux -- $^{18}$Ne stored at $\gamma=100$)
\item {\tt BB100flux\_He.dat} ($\beta$-beam neutrino flux -- $^{6}$He stored at $\gamma=100$)
\item {\tt BeamBckg\_100.dat} (beam background)
\item {\tt AtmBckg\_100.dat} (atmospheric background)
\item {\tt Mig\_WC\_numu.dat} (migration matrix -- $\nu_\mu$)
\item {\tt Mig\_WC\_numubar.dat} (migration matrix -- $\bar{\nu}_\mu$)
\item {\tt Mig\_WC\_nue.dat} (migration matrix -- $\nu_e$)
\item {\tt Mig\_WC\_nuebar.dat} (migration matrix -- $\bar{\nu}_e$)
\item {\tt XCC\_Nuance.dat} (charged current cross sections)
\item {\tt XNC\_Nuance.dat} (neutral current cross sections)
\item {\tt Null.dat} (auxiliary file)
\ei
The neutrino beam is produced at CERN and directed towards a a megaton Water Cerenkov detector at Fr\'{e}jus. 
The neutrinos originate from the decays of accelerated isotopes $^{18}$Ne ($\nu_e$) and $^6$He ($\bar{\nu}_e$).
The acceleration factor is $\gamma=100$ for both types of isotopes and $2.2\cdot10^{18}$ $^{18}$Ne decays per
year and $5.8\cdot10^{18}$ $^{6}$He decays per year are assumed. The CERN-Fr\'{e}jus baseline is L~=~130~km, the
fiducial mass of the detector is $\mathrm{m_{det} = 500 \,kt}$ and 4~years $\nu$-running and 4~years
$\bar{\nu}$-running are assumed. The energy resolution is introduced manually by
four migration matrices (for $\nu_e , \bar{\nu}_e ,\nu_{\mu} ,\bar{\nu}_\mu$) that describes energy smearing mainly
from Fermi Motion. The following rules are defined within {\tt BB\_100.glb}:
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance -- $^{18}$Ne stored} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $0.707 \, \otimes \, (\nu_e\rightarrow\nu_e)_{\mathrm{CC}}$ & & 0.02 & $10^{-4}$ \\
 & & & & \\
Background & $4.3\cdot 10^{-5} \, \otimes \, (\nu_e \rightarrow \nu_e)_\mathrm{CC}$ & & 0.02 & $10^{-4}$ \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance -- $^{18}$Ne stored} & & \\ \hline
Signal & $1.0 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$ & (energy dep. efficiency) & 0.02 & $10^{-4}$ \\
 & & & & \\
Background & $1.0 \, \otimes \, (\nu_e \rightarrow \nu_x)_\mathrm{NC}$ & (from external file) & 0.02 & $10^{-4}$ \\
Atm. background & & (from external file) & 0.02 & $10^{-4}$ \\ \hline \hline
\multicolumn{3}{|l|}{Disappearance -- $^6$He stored} & &  \\ \hline
Signal & $0.677 \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_{\mathrm{CC}}$ & & 0.02 & $10^{-4}$ \\
 & & & & \\
Background & $4.3\cdot 10^{-5} \, \otimes \, (\bar{\nu}_e \rightarrow \nu_e)_\mathrm{CC}$ & & 0.02 & $10^{-4}$ \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance -- $^6$He stored} & & \\ \hline
Signal & $1.0 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & (energy dep. efficiency) & 0.02 & $10^{-4}$ \\
 & & & & \\
Background & $1.0 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & (from external file) & 0.02 & $10^{-4}$ \\
Atm. background & & (from external file) & 0.02 & $10^{-4}$ \\ \hline \hline
\end{tabular}
\end{center}

>>>>

{\tt @signalerror = 10.:0.0001}. In case of systematics switched on the systematics functions {\tt chiSpectrumTilt}

@@

For the disappearance channels only the QE sample is used since statistics is already quite large and a treatment as for the
appearance channels would only slightly modify the results. The quantitative treatment of systematics is similar to \cite{Ishitsuka:2005qi}. The following rules are 

@@

The \SPL\ experiment can be simulated with the file {\tt SPL.glb}. This file was used in \cite{Campagne:2006yx}
and follows the experiment description from \cite{Mezzetto:2003mm, Campagne:2004wt}. These references
should be cited if the file {\tt SPL.glb} is used for a scientific publication or a talk. For calculations that
involve {\tt SPL.glb}, the following additional files are required: 
\bi
\item {\tt SPLplus.dat} (neutrino flux from CERN -- $\nu_\mu$)
\item {\tt SPLminus.dat} (neutrino flux from CERN -- $\bar{\nu}_\mu$)
\item {\tt Mig\_WC\_numu.dat} (migration matrix -- $\nu_\mu$)
\item {\tt Mig\_WC\_numubar.dat} (migration matrix -- $\bar{\nu}_\mu$)
\item {\tt Mig\_WC\_nue.dat} (migration matrix -- $\nu_e$)
\item {\tt Mig\_WC\_nuebar.dat} (migration matrix -- $\bar{\nu}_e$)
\item {\tt XCC\_spl.dat} (charged current cross sections)
\item {\tt XNC\_spl.dat} (neutral current cross sections)
\ei
The \SPL\ experiment uses a neutrino beam from the CERN to Fr\'{e}jus. The target power is 
4~MV and 2~years $\nu$-running and 8~years $\bar{\nu}$-running 
is assumed. The fiducial mass of the Water Cerenkov detector is taken to be 
$\mathrm{m_{det} = 500 \,kt}$ at a baseline of L~=~130~km. The energy resolution is introduced manually by
four migration matrices (for $\nu_e , \bar{\nu}_e ,\nu_{\mu} ,\bar{\nu}_\mu$) that describe energy smearing 
due to Fermi Motion. The following rules are defined within {\tt SPL.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance (+)} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline 
Signal & $1.0 \, \otimes \, (\nu_\mu\rightarrow\nu_\mu)_{\mathrm{CC}}$ & (energy dep. efficiency) & 0.02 & $10^{-4}$\\
 & &  & &\\
Background & $4.3\cdot 10^{-5} \, \otimes \, (\nu_\mu \rightarrow \nu_\mu)_\mathrm{CC}$ & & 0.02 & $10^{-4}$ \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance (+)} &  & \\ \hline
Signal & $0.707 \, \otimes \, (\nu_\mu\rightarrow \nu_e)_\mathrm{CC}$ & & 0.02 & $10^{-4}$\\
&&&&\\
Background & $6.5\cdot 10^{-4} \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & $5.4\cdot 10^{-4} \, \otimes \, (\nu_\mu \rightarrow \nu_\mu)_\mathrm{CC}$ & 0.02 & $10^{-4}$ \\
 & $0.7 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_e )_\mathrm{CC}$ & & 0.02 &  $10^{-4}$ \\
Beam Background & $0.677 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_e )_\mathrm{CC}$ & $0.707 \, \otimes \, (\nu_e \rightarrow \nu_e )_\mathrm{CC}$ & 0.02 & $10^{-4}$ \\ \hline \hline
\multicolumn{3}{|l|}{Disappearance (--)} & & \\ \hline 
Signal & $1.0 \, \otimes \, (\bar{\nu}_\mu\rightarrow\bar{\nu}_\mu)_{\mathrm{CC}}$ & (energy dep. efficiency) & 0.02 & $10^{-4}$\\
 & &  & &\\
Background & $4.3\cdot 10^{-5} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & & 0.02 & $10^{-4}$ \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance (--)} &  & \\ \hline
Signal & $0.677 \, \otimes \, (\bar{\nu}_\mu\rightarrow \bar{\nu}_e)_\mathrm{CC}$ & & 0.02 & $10^{-4}$\\
&&&&\\
Background & $0.0025 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & $5.4\cdot 10^{-4} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & 0.02 & $10^{-4}$ \\
 & $0.7 \, \otimes \, (\nu_\mu \rightarrow \nu_e )_\mathrm{CC}$ & & 0.02 &  $10^{-4}$ \\
Beam Background & $0.677 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_e )_\mathrm{CC}$ & $0.707 \, \otimes \, (\nu_e \rightarrow \nu_e )_\mathrm{CC}$ & 0.02 & $10^{-4}$ \\ \hline \hline
\end{tabular}
\end{center}

@@

The file {\tt Reactor1.glb} allows to simulate a small $\bar{\nu}_e$-disappearance reactor experiment. The basic
version of this file was used within \cite{Huber:2003pm} which should be cited if the file {\tt Reactor1.glb} is
used for a scientific publication or a talk. For calculations that involve {\tt Reactor1.glb}, the following
additional files are required:
\bi
\item {\tt Reactor.dat} (neutrino flux from reactor)
\item {\tt XCCreactor.dat} (charged current cross sections for low energies)
\ei
The neutrino source is the core of a nuclear power reactor. The integrated luminosity is assumed to be
$\mathrm{\mathcal{L} = 400 \,t \, GW\, yr}$, \eg\ a 20~t detector, a reactor with a thermal power of 4~GW
and a running period of 5 years. As detector technology, a liquid scintillator 
detector is assumed, a far detector at a baseline of L~=~1.7~km and a near detector which is
assumed to be identical to the far detector (maybe apart from the size) in order to minimize the impact of systematical uncertainties. The normalization error
used in the file {\tt Reactor1.glb} has to be considered as an effective error, receiving contributions from
individual uncertainties (see~\cite{Huber:2003pm}). The energy resolution is
$\mathrm{\sigma_e=5\%\cdot\sqrt{E_{vis}}}$ and the choice for {\tt @sigma\_function} is {\tt \#inverse\_beta}. The following rules are defined within {\tt Reactor1.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline 
Signal & $1.0 \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_{\mathrm{CC}}$ & \hspace{5.5cm} & 0.008 & 0.005\\
 & &  & &\\
Background & $5.8\cdot 10^{-5} \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_\mathrm{CC}$ & \hspace{5.5cm} &
$10^{-6}$ & $10^{-6}$ \\ \hline \hline 
\end{tabular}
\end{center}

@@

The files {\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb} allow to simulate the \DC\ reactor experiment in France. 
The basic versions of these files were used within \cite{Huber:2006vr}, which should be cited if the files 
{\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb} are
used for a scientific publication or a talk. For calculations that involve {\tt D-Chooz\_near.glb} and/or {\tt D-Chooz\_far.glb}, the following
additional files are required:
\bi
\item {\tt Reactor.dat} (neutrino flux from reactor)
\item {\tt XCCreactor.dat} (charged current cross sections for low energies)
\ei
The \DC\ experiment is located at the Chooz reactor complex, and the two reactor cores serve as $\bar{\nu}_e$
neutrino source, so the thermal power is $\mathrm{2\cdot4.2\,GW}$. Two identical liquid scintillator detectors
with a fiducial mass of $\mathrm{m_{det} = 10.16 \,t}$ are used as near and far detector. The far detector
is planned to be located in the {\sc Chooz} cavern at a baseline of L~=~1.05~km from the two reactor cores and
the near detector is assumed to be located at a distance of 0.1~km to the cores. The total running time of the
experiment is assumed to be 5 years. So, the integrated luminosity at the far detector yields $\mathrm{\mathcal{L} \approx
427 \,t \, GW\, yr}$.
Here, the total running time of 5 years is assumed within {\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb}, so near
and far detector are assumed to start the mode of operation simultaneously. For the simulation of \DC\ and
considering a delayed start of data taking at the near detector the file {\tt D-Chooz\_near.glb} has to be
modified. The cancellation of systematical uncertainties is considered by the manual definition of a $\chi^2$
as described in \cite{Huber:2006vr} with the treatment of user-defined systematics as described in \Sec~\ref{sec:userchi}   
The energy resolution is
$\mathrm{\sigma_e=5\%\cdot\sqrt{E_{vis}}}$ and the choice for {\tt @sigma\_function} is {\tt \#inverse\_beta}. The following rules are defined within {\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|c|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance} & $\sigma_\mathrm{flux}$ & $\sigma^N_\mathrm{fid}$ & $\sigma^F_\mathrm{fid}$ &
$\sigma^N_\mathrm{cal}$ & $\sigma^F_\mathrm{cal}$ \\ \hline 
Signal & $1.0 \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_{\mathrm{CC}}$ & & 0.02 & 0.006 & 0.006 & 0.005 &
0.005 \\
 & & & & & & & \\
Background & neglected & (sys. dominates) & -- & -- & -- & -- & -- \\ \hline \hline 
\end{tabular}
\end{center}

@@

The $\gamma=100$ $\beta$-beam baseline scenario from CERN to Fr\'{e}jus can be simulated with the file {\tt
BB\_100.glb}. The basic version of this file was used within \cite{Campagne:2006yx}. This reference
should be cited if the file {\tt BB\_100.glb} is used for a scientific publication or a talk. For calculations that
involve {\tt BB\_100.glb}, the following additional files are required: 
\bi
\item {\tt BB100flux\_Ne.dat} ($\beta$-beam neutrino flux -- $^{18}$Ne stored at $\gamma=100$)
\item {\tt BB100flux\_He.dat} ($\beta$-beam neutrino flux -- $^{6}$He stored at $\gamma=100$)
\item {\tt BeamBckg\_100.dat} (beam background)
\item {\tt AtmBckg\_100.dat} (atmospheric background)
\item {\tt Mig\_WC\_numu.dat} (migration matrix -- $\nu_\mu$)
\item {\tt Mig\_WC\_numubar.dat} (migration matrix -- $\bar{\nu}_\mu$)
\item {\tt Mig\_WC\_nue.dat} (migration matrix -- $\nu_e$)
\item {\tt Mig\_WC\_nuebar.dat} (migration matrix -- $\bar{\nu}_e$)
\item {\tt XCC\_Nuance.dat} (charged current cross sections)
\item {\tt XNC\_Nuance.dat} (neutral current cross sections)
\item {\tt Null.dat} (auxiliary file)
\ei
The neutrino beam is produced at CERN and directed towards a a megaton Water Cerenkov detector at Fr\'{e}jus. 
The neutrinos originate from the decays of accelerated isotopes $^{18}$Ne ($\nu_e$) and $^6$He ($\bar{\nu}_e$).
The acceleration factor is $\gamma=100$ for both types of isotopes and $2.2\cdot10^{18}$ $^{18}$Ne decays per
year and $5.8\cdot10^{18}$ $^{6}$He decays per year are assumed. The CERN-Fr\'{e}jus baseline is L~=~130~km, the
fiducial mass of the detector is $\mathrm{m_{det} = 500 \,kt}$ and 4~years $\nu$-running and 4~years
$\bar{\nu}$-running are assumed. The energy resolution is introduced manually by
four migration matrices (for $\nu_e , \bar{\nu}_e ,\nu_{\mu} ,\bar{\nu}_\mu$) that describe the energy smearing 
due to Fermi Motion. The following rules are defined within {\tt BB\_100.glb}:
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance -- $^{18}$Ne stored} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $0.707 \, \otimes \, (\nu_e\rightarrow\nu_e)_{\mathrm{CC}}$ & & 0.02 & $10^{-4}$ \\
 & & & & \\
Background & $4.3\cdot 10^{-5} \, \otimes \, (\nu_e \rightarrow \nu_e)_\mathrm{CC}$ & & 0.02 & $10^{-4}$ \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance -- $^{18}$Ne stored} & & \\ \hline
Signal & $1.0 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$ & (energy dep. efficiency) & 0.02 & $10^{-4}$ \\
 & & & & \\
Background & $1.0 \, \otimes \, (\nu_e \rightarrow \nu_x)_\mathrm{NC}$ & (from external file) & 0.02 & $10^{-4}$ \\
Atm. background & & (from external file) & 0.02 & $10^{-4}$ \\ \hline \hline
\multicolumn{3}{|l|}{Disappearance -- $^6$He stored} & &  \\ \hline
Signal & $0.677 \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_{\mathrm{CC}}$ & & 0.02 & $10^{-4}$ \\
 & & & & \\
Background & $4.3\cdot 10^{-5} \, \otimes \, (\bar{\nu}_e \rightarrow \nu_e)_\mathrm{CC}$ & & 0.02 & $10^{-4}$ \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance -- $^6$He stored} & & \\ \hline
Signal & $1.0 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & (energy dep. efficiency) & 0.02 & $10^{-4}$ \\
 & & & & \\
Background & $1.0 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & (from external file) & 0.02 & $10^{-4}$ \\
Atm. background & & (from external file) & 0.02 & $10^{-4}$ \\ \hline \hline
\end{tabular}
\end{center}
